Verification of concurrent design patterns with data

### 2019-02-15 2018-Arch-pNets/arch-pNets.tex

A few tracks, pas r\'edig\'es...

@@

infinite/parametrized model checking? == ERIC + Simon
Basic models for data-sensitive infinite systems: Hennesy \& Lin's value-passing systems with assignments \cite{CONCUR::Lin1996,HennessyL1995:353,APSEC::Lin2001}

various classe infinite-state systems and/or paramaterized topologies
via predicate abstraction and SMT satisfiability:
\cite{BruniEtAl-Tiles-Concur2000,DBLP:conf/cade/GhilardiNRZ08,DBLP:journals/corr/CimattiGMT13,DBLP:journals/corr/abs-1806-11459}

>>>>

%%A few tracks, pas r\'edig\'es...

@@

%% infinite/parametrized model checking? == ERIC (listes ci-dessous)  + Simon

Basic research on behaviour models and verification algorithms for
data-sensitive systems started in the nineties, with the seminal work
of Hennesy, Lin, and their colleagues on value-passing systems with
assignments
\cite{CONCUR::Lin1996,HennessyL1995:353,APSEC::Lin2001}. Later, many
different works addressing various classes of infinite-state systems
and/or paramaterized topologies have been published, using
combinations of approaches, often including predicate abstraction and
SMT satisfiability (see
e.g. \cite{BruniEtAl-Tiles-Concur2000,DBLP:conf/cade/GhilardiNRZ08,DBLP:journals/jsat/AlbertiGPRR12,CimattiEtAl-NUXMV-CAV2014,ChampionEtAl-Kind2-CAV2016}). With
respect to these, we use symbolic representations not only to get a
finite representation of infinite spaces, but also to express the
(data-sensitive) synchronisations with the environment, making our
models suitable for compositional verification.

Among these works, several have shown the capacity of the SMT engines
(either Z3 or Yikes) as servers for solving verification conditions of
the algorithms, for large case-studies
(e.g. \cite{DBLP:journals/corr/CimattiGMT13,DBLP:journals/corr/abs-1806-11459}).
%% SMT on an application not using component structure. is there a strong Z3 example == Eric
